Real-Time Scheduling Algorithms and Battery Consumption of Mobile Devices

### 2017-03-19 paper-RMDON.tex
Update paper-RMDON.tex

>>>>

\bibitem{ahmed-chakrabarti}J.~Ahmed and C.~Chakrabarti, \emph{A dynamic task scheduling algorithm for battery powered DVS systems}, 2004 IEEE International Symposium on Circuits and Systems, Vancouver, BC, 2004. doi: 10.1109/ISCAS.2004.1329396

\bibitem{rao-et-al} V.~Rao, N.~Navet and G.~Singhal, \emph{Battery aware dynamic scheduling for periodic task graphs}. 2006 Proceedings 20th IEEE International Parallel \& Distributed Processing Symposium, Rhodes Island, 2006. doi: 10.1109/IPDPS.2006.1639403
